--- 
title: "Check for GitHub Username Appropriateness"
author: "YuXin Xie"
date: "`r Sys.Date()`"
output: 
  html_document:
  theme: united
  highlight: tango
---


## Shiny App
```{r eval=T}

library(shiny)

check_username=function(username,first_name=NA,last_name=NA,topic_word=NA){
  gchara=c(0:9,"-","_",LETTERS,letters)
  x=strsplit(username,split = "")
  x=x[[1]]
  y=x[length(x)]
  sum=sum(x%in%(0:9))
  s1="请输入您的用户名。"
  s2="请考虑去掉后面的数字。"
  s3="请考虑改进一下。"
  s4="这个用户名太长了。"
  s5="这是一个很好的用户名。"
  i1=ifelse(length(x)>30,s4,s5)
  i2=ifelse(y%in%(0:9),s2,i1)
  i3=ifelse(sum==length(x),s3,i2)
  suggests=ifelse(length(x)>0,i2,s1)
  return(suggests)
}

ui = fluidPage(
  sidebarLayout(
    sidebarPanel(
      
      textInput("username","Please input your username.",value = ""),   
      textInput("last_name","Please input your last_name",value = ""),
      textInput("first_name","Please input your first_name",value = "")
    ),
    mainPanel(
      
      h2("Your username"),
      verbatimTextOutput("username"),
      br(),
      
      h2("Our evaluation"),
      verbatimTextOutput("evaluation"),
      br(),
      
      h2("Our suggestions"),
      verbatimTextOutput("suggestions"),
      br()
      
    )
  )
)

server = function(input,output){
  output$username=renderText({
    input$username
  })
  output$evaluation=renderText({
    check_username(input$username)
  })
  output$suggestions=renderText({
    paste0(input$first_name,input$last_name)
  })
}

shinyApp(ui=ui,server=server,options=list(display.mode="showcase"))


```

## Function Description

Given a GitHub username, check for its appropriateness and give suggested usernames if certain rules are violated. 

**Usage**
```
check_username(username, first_name=NA, last_name=NA, topic_word=NA)

```

- Inputs
    - required: 
        - `username`: GitHub username, e.g. "WinnerHaha2018"
    - optional: 
        - `first_name`: user's first name, e.g. Wenliang
        - `last_name`: user's last name, e.g. He
        - `topic_word`: a topic name, if the account is created for a specific topic, e.g. Education, Statistics
- Outputs
    - print to screen the appropriateness of a username
        - "This is a good username to use."
        - "Please consider improving it a bit."
        - "Please use a different username."
    - print to screen rules that are violated
        - "Please do not use characters other than 0-9, a-z, A-Z, - and _"
        - "Please consider removing the trailing numbers"
    - `suggests`: a list of suggested usernames if certain rules are violated and user information provided


## Details

Rules that are implemented:

- DO NOT
    - `MUST`:  usernames composed completely of numbers
- NOT RECOMMENDED
    - `MUST`: usernames with trailing numbers
    - `MORE`: usernames that are overly long (e.g. more than 30 characters)
- RECOMMENDED
    - use your actual names

## Examples

- Function Definition
```{r eval=T}
## define your function here

check_username=function(username,first_name=NA,last_name=NA,topic_word=NA){
  gchara=c(0:9,"-","_",LETTERS,letters)
  x=strsplit(username,split = "")
  x=x[[1]]
  y=x[length(x)]
  sum=sum(x%in%(0:9))
  s1="请输入您的用户名。"
  s2="请考虑去掉后面的数字。"
  s3="请考虑改进一下。"
  s4="这个用户名太长了。"
  s5="这是一个很好的用户名。"
  i1=ifelse(length(x)>30,s4,s5)
  i2=ifelse(y%in%(0:9),s2,i1)
  i3=ifelse(sum==length(x),s3,i2)
  suggests=ifelse(length(x)>0,i2,s1)
  return(suggests)
}

```

- Examples
```{r eval=T}
## a username composed completely of numbers
check_username(username="1237564", first_name="Wenliang", last_name="He", topic_word="Education")

```


```{r eval=T}
## a username with trailing numbers
check_username(username="WinnerHaha2018", first_name="Wenliang", last_name="He")

```


## Things to Do

- Include one more hard rule for extra credits.
- Write a shiny app to host the function online.


## References

- [Tips for GitHub Usernames](https://quantbook.netlify.com/index.html#register-a-github-account)


----

## Grading Criteria


| Topic | Excellent: 3 | Satisfactory: 2 | Needs Work: 1 |
|---|---|---|---|
| 1. Completeness | complete code | sufficient | incomplete | 
| 2. Coding Strategy | excellent coding strategy | satisfactory | poor |
| 3. Coding Style | excellent coding style | satisfactory | poor |
| 4. Presentation | effective presentation | satisfactory | poor |
| 5. Access | easy access | satisfactory | poor | 
| Extra Credits: Mastery | exceptional mastery | satisfactory | poor |  


**Complete Code**

- **complete**: two `MUST` and two `MORE` are done
- **sufficient**: two `MUST` are done
- **incomplete**: at least one `MUST` is not done

**Excellent Coding Strategy** 

- code is corrent and minimal (i.e. avoiding repetitive code) 
    - e.g. break a complicated problem into simpler sub-problems
    - e.g. use appropriate data structure (e.g. vector, matrix, dataframe, list)

**Excellent Coding Style** 

- code is easily readable
    - e.g. use of effective indentation and spacing
    - e.g. use appropriate comments

**Effective Presentation**

- provide good examples to illustrate usage of the function
- writing is clear and concise
- overall view is beautiful

**Easy Access**

- upload project to GitHub 
- make it easy for instructor and TA(s) to access source code 
- create shiny app to deploy the code 


**Extra Credits: Exceptional Mastery**

- the task is ambitionous (e.g. including new ideas way beyond the starter code)
- exhibit extraordinary effort
- demonstrate usually sophisticated application of techniques/tools from this course
- use additional techniques/tools not addressed by this course

In short, "exceptional mastery" goes beyond what is commonly expected!




